Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-01-02 p2/p2.Rmd
.
fp fn definitions

## The Chumbley Score Test

@@

## Testing setup:
\hh{Using cross-validation setup to identify appropriate parameter settings for (a) signatures and (b) profiles directly}

@@

```{r }
library(kableExtra)
a27<- all %>% filter(wo==200, wv==30) %>% xtabs(data= ., ~signif+match)
knitr::kable(a27, digits=0, caption = "Window of Optimization 320 and Window of Validation 50", format = "latex" ,booktabs=TRUE)%>% kableExtra::kable_styling(latex_options = c("hold"))

@@

```{r}
a27<- all %>% filter(wo==120, wv==30) %>% xtabs(data= ., ~signif+match)
knitr::kable(a27, digits=0, caption = "Window of Optimization 120 and Window of Validation 50", format = "latex" ,booktabs=TRUE)%>% kableExtra::kable_styling(latex_options = c("hold"))
```

```{r}
a27<- all %>% filter(wo==80, wv==30) %>% xtabs(data= ., ~signif+match)
knitr::kable(a27, digits=0, caption = "Window of Optimization 80 and Window of Validation 50", format = "latex" ,booktabs=TRUE)%>% kableExtra::kable_styling(latex_options = c("hold"))
```

>>>>

# The Chumbley Score Test

@@

## Testing setup
\hh{Using cross-validation setup to identify appropriate parameter settings for (a) signatures and (b) profiles directly}

@@

```{r }
library(kableExtra)
a27<- all %>% filter(wo==200, wv==30) %>% xtabs(data= ., ~signif+match)
a27<- as.data.frame(a27)
a27$Type<- c("True Negative","False Positive (Type I)","False Negative (Type II)","True Positive")
knitr::kable(a27, digits=0, caption = "Window of Optimization 320 and Window of Validation 50", format = "latex" ,booktabs=TRUE)%>% kableExtra::kable_styling(latex_options = c("hold"))

@@

```{r}
a27<- all %>% filter(wo==120, wv==30) %>% xtabs(data= ., ~signif+match)
a27<- as.data.frame(a27)
a27$Type<- c("True Negative","False Positive (Type I)","False Negative (Type II)","True Positive")
knitr::kable(a27, digits=0, caption = "Window of Optimization 120 and Window of Validation 50", format = "latex" ,booktabs=TRUE)%>% kableExtra::kable_styling(latex_options = c("hold"))
```

```{r}
a27<- all %>% filter(wo==80, wv==30) %>% xtabs(data= ., ~signif+match)
a27<- as.data.frame(a27)
a27$Type<- c("True Negative","False Positive (Type I)","False Negative (Type II)","True Positive")
knitr::kable(a27, digits=0, caption = "Window of Optimization 80 and Window of Validation 50", format = "latex" ,booktabs=TRUE)%>% kableExtra::kable_styling(latex_options = c("hold"))
```
